The Formation and Evolution of Compact Core Galaxies in the RESOLVE Survey

### 2016-04-17 paperdraft.tex
updates to paper

\documentclass[iop,apj,twocolappendix]{emulateapj}
\pdfoutput=1 %for arxiv submission to use pdf
\usepackage{apjfonts}
\usepackage{natbib}
\usepackage{amsmath,amstext,textcomp}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
\usepackage[all]{hypcap} %Links go to figures. This breaks deluxetables; use \capstartfalse \capstarttrue around deluxetables to fix it.
\renewcommand{\sectionautorefname}{\S} %for \autoref
\renewcommand{\subsectionautorefname}{\S} %for \autoref
\renewcommand{\subsubsectionautorefname}{\S} %for \autoref

@@

\item[The initial input file]{The initial input file tells \textsc{Galfit} where to find the image, PSF, mask, and constraint, and also holds the initial guesses for our fit parameters. These initial parameters can just be rough guesses, but for our purposes, we use the previously derived photometric data for RESOLVE galaxies as our initial guesses (see \autoref{phot} for more details). For the one component fits, we set up our input file to have a section for measuring the value of the sky background, and another section for fitting a S\'ersic profile to galaxy. The two component fits with have three sections -- the sky and S\'ersic as in the one component fits, plus a second S\'ersic fit. }

@@

\item[The mask image]{The first step is to create a mask image that has the same dimensions as our input image with each pixel value as zero. We again use Source Extractor to compile a list of all the objects in the input image, and then use this list to replace the pixel values in our mask with one. We replace the areas of the mask that have detected sources with ones, thus creating a binary image. \textsc{Galfit} uses the mask image to }

\item[The constant file]{The constraint file hosts the limits we are willing to accept for our fits. We fit on the following galaxy parameters: x \& y position in the image, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle. The constraints in place for these variables are listed in \autoref{constrtable}.}

@@

\begin{table}[htdp]
\begin{center}
\begin{tabular}{cc} \hline
parameter & constaint  \\ \hline
x \& y position & $\pm5$ pixels from input value \\
integrated magnitude & 0 -- 40 \\ 
\Reff\ & 0.2 -- 750 pixels \\ 
S\'ersic n & 0.1 -- 8 \\ 
axial ratio & 0 -- 1 \\
position angle & -360 -- 360 \\ \hline

\end{tabular}
\end{center}
\caption{Summary of the constraints imposed on our \textsc{Galfit} models.}
\label{constrtable}
\end{table}%

With the one and two component fits from \textsc{Galfit} in hand, we compare the reduced chi-square values for each fit and determine where the two component fit provides a significant improvement to the reduced chi-square of the one component fit. With each galaxy now having either a one or two component fit, we select objects that have a one component radius $<800$ pc  or have a two component core radius $<800$ pc. The core will be the smaller of the two components fit by \textsc{Galfit}.

\subsubsection{Selection of CCGs}
\label{ccgsel}

\noindent We use the AIMSS sample to select a maximum radius for our CCGs: 800 pc. This upper limit ensures that we are selecting the most compact galaxies in RESOLVE, but also lets us select a range of CSSs, including cEs and dEs. RESOLVE's lower stellar mass limit (quote, and include in RESOLVE section above) restricts us from reaching down to UCD masses.

Our sample is thus comprised of XX CCGs without envelopes (XX from RESOLVE-A, and XX from RESOLVE-B and XX CCGs with envelopes (XX from RESOLVE-A and XX from RESOLVE-B). Figure 1 shows their distribution in stellar mass and \Reff\ compared to other RESOLVE galaxies and the AIMSS CSSs.

\section{Data and Methods}
\label{methods}

\subsection{Photometry: colors, stellar masses, and star formation rates}
\label{phot}
\noindent The RESOLVE survey overlaps with a variety of photometric surveys, including GALEX NUV, SDSS $ugriz$, and UKIDSS $YHK$ and 2MASS $JHK$, and has HI data from ALFALFA and its own pointed observations with the Greenbank Telescope and Arecibo. \citet{Eckert2015} describes in detail RESOVLE's custom reprocessing for these photometry, but the basic steps are described here.

\subsection{Environmental Metrics}
\label{env}
\noindent RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments. \citet{Moffett2015}

@@

\subsubsection{SOAR spectroscopy}
\noindent The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile. We employ the Goodman Spectrograph, designed and built by UNC, along with RESOLVE's custom-built image slicer with 3 $1''$ slits to observe galaxies in both a broad setup and either an emission- or absorption-line kinematic setup. From this absorption-line setup, we are able to derive velocity dispersions. We use the supremely-efficient 2100 l/mm VPH grating and cover a wavelength range 4858-5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335. To achieve S/N $\sim$ 25 per \AA, we bin each central spectrum to \Reff.

The

@@

The spectral reduction proceeds as follows. Using the standard IRAF Gemini-GMOS data packages, bias and overscan subtraction, spatial trimming, flat fielding and fiber identification are performed. We next use the GMOS package gemCRspec, a wrapper for \texttt{LA\_COSMIC}, to clean cosmic rays from each science exposure. We then correct the science frames for quantum efficiency differences between CCDs. Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed. We then stack the individal fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$. More information on the data reduction for the Gemini GMOS IFU can be found in the Appendix A.

@@

\noindent We then derive the velocity dispersion ($\sigma$) from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}. This code fits many model spectra (cite Maraston) to the observed input spectrum.

@@

\subsection{Colors and Star formation rates}
\noindent 
* FIGURE: FSMGR vs Mbary/stars for RESOLVE, CCGs, and AIMSS \\
* FIGURE: SFR vs. Mbary/stars for RESOLVE, CCGs, and AIMSS \\

\noindent Figure \#A shows the u-r colors of our CCG sample plotted against M$_{\rm bary}$, compared to the RESOLVE sample as a whole. An unsual finding is that XX CCGs live on the blue sequence, a previsouly rare color for CSSs. REF and REF have previously found UCDs in the blue cloud but most cEs and dEs are typically thought of as being "red and dead".

Figure \#B shows FSMGR vs. M$_{\rm bary}$ for the same objects. As with the colors, we find that many (XX\%) of CCGs are forming stars at a rapid rate ( XX per Gyr). This again goes against the common thought that CSSs are ``red and dead".

Here discuss more the envelope vs non-enveloped CCGs and how their popultions may differ.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CCG formation and evolution} %kind of like a discussion section

@@

>>>>

\documentclass[iop,apj]{emulateapj}
\pdfoutput=1 %for arxiv submission to use pdf
\usepackage{apjfonts}
\usepackage{natbib}
\usepackage{epstopdf}
\usepackage{amsmath,amstext,textcomp}
\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
\usepackage[all]{hypcap} %Links go to figures. This breaks deluxetables; use \capstartfalse \capstarttrue around deluxetables to fix it.
\renewcommand{\sectionautorefname}{\S} %for \autoref
\renewcommand{\subsectionautorefname}{\S} %for \autoref
\renewcommand{\subsubsectionautorefname}{\S} %for \autoref

@@

\item[The initial input file]{The initial input file tells \textsc{Galfit} where to find the image, PSF, mask, and constraint, and also holds the initial guesses for our fit parameters. These initial parameters can just be rough guesses, but for our purposes, we use the previously derived photometric data for RESOLVE galaxies as our initial guesses (see \autoref{phot} for more details). For the one component fits, we set up our input file to have a section for measuring the level of the sky background, and another section for fitting a S\'ersic profile to galaxy. The S\'ersic model will find a best fit for the following parameters: central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle.}

@@

\item[The mask image]{The first step in making the mask is to create an image that has the same dimensions as our input image but with each pixel value equaling zero. We again use Source Extractor to compile a list of all the objects in the input image, and  use this list to replace the pixel values at the coordinates of the located objects with one. \textsc{Galfit} uses the mask image to ignore any objects neighboring our galaxy while it is completing the fit.}

\item[The constant file]{The constraint file hosts the limits we are willing to accept for each of the fit parameters. The constraints for x \& y position in the image, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle for the one component fits are listed in \autoref{constrtable}. }

@@

\begin{table}[htdp]
\begin{center}
\begin{tabular}{cc} \hline
parameter & constaint  \\ \hline
x \& y position & $\pm5$ pixels from input value \\
integrated magnitude & 0 -- 40 \\ 
\Reff\ & 0.2 -- 750 pixels \\ 
S\'ersic n & 0.1 -- 8 \\ 
axial ratio & 0 -- 1 \\
position angle & -360 -- 360 \\ \hline
\end{tabular}
\end{center}
\caption{Summary of the constraints imposed on our \textsc{Galfit} models.}
\label{constrtable}
\end{table}%

We use all of the above to obtain a one component, deconvolved fit for every galaxy in the RESOLVE survey. We then perform the two component fits as follows. We use the output of the one component fit as the basis of the input file for the two component fit. The first two sections in the two component fit initial input file will be identical to the output of the one component fit (except that the names of the files to be output are changed). We then add a third section to include a second S\'ersic fit, and change the initial guess for \Reff\ to be double that of the one component best fit. This gives \textsc{Galfit} an idea to fit on both a core and envelope. The PSF, image, and mask image will all be the same as before. We add to the constraint file the same constraints as listed in \autoref{constrtable}, but for the third section. In other words, there will be two sets of constraints in the file now, with the first set applying to the first S\'ersic fit and the second set applying the second S\'ersic fit. The constraints for each parameter are the same for both sets. We do not further constrain the two component fits since we are looking for general fits to the wide variety of galaxies in RESOLVE and do not want to over constrain our fits.

For both the one and two component fits, \textsc{Galfit} outputs a text file with the best fits for central x \& y position of the model, integrated magnitude, \Reff, S\'ersic n, axial ratio (b/a), and position angle and a $\chi^2/\nu$ as well as a fits file that contains the data, best fit model, and residual images. Figure XX shows the output for three different galaxies in RESOLVE.

\subsubsection{Selection of CCGs}

Now that we have seeing-deconvolved \Reff\ values for the entire RESOLVE sample, we begin our search for compact core galaxies. We use the AIMSS sample to select a maximum cutoff core-only radius for CCGs at 800 pc. This upper limit ensures that we are selecting the most compact galaxies in RESOLVE, but also lets us select a range of CSSs, including cEs and dEs. RESOLVE's lower stellar mass limit of  restricts us from reaching down to UCD masses.

We start our search for CCGs by using the one component fit from the above analysis and select galaxies with \Reff\ values $<1000$ pc. Since we are looking for galaxies with compact cores, going up to \Reff\ $\sim 1000$ pc allows us to select objects with cores that are dominating the light and therefore may have a smaller core \Reff\ in a two component fit. We also limit the  $\chi^2/\nu$ to be $<1.3$, since values above this represent galaxies with large residuals left over, which are spirals or irregulars that we would not consider ``cored". After this selection, we are left with 124 galaxies in the CCG candidate sample.

Next, we perform new two component fits using different fitting constraints: (1) the central x and y positions are taken from the one component fit and are held constant for both S\'ersic components, (2) the \Reff\ of the second S\'ersic fit is constrained to always be larger than that of the first S\'ersic fit, and (3) the S\'ersic n of the second component is held constant at 1 for an exponentially decreasing disk profile. We let the values of \Reff, the integrated magnitude, b/a ratio, and PA change for both fits. By doing this, we are forcing \textsc{Galfit} to fit on a core (the first S\'ersic fit) and disky envelope (the second S\'ersic fit) for each CCG candidate.

We then examine the fits by eye and create our final CCG sample by selecting where the core \Reff\ $< 800$ pc and $\chi^2/\nu < 1.3$ to again exclude poor fits. Our sample is thus comprised of 96 CCGs in total (63 from RESOLVE-A and 33 from RESOLVE-B). This represents $\sim6$\% of the total RESOLVE galaxy sample. \autoref{fig:radius} shows their distribution in stellar mass and decomposed \Reff\ compared to other RESOLVE galaxies and the AIMSS cEs and dEs. For the RESOLVE sample, we are plotting the one component fits

We quantify the amount of light in the core vs. the envelope by taking a ratio of the fluxes of the core and the envelope. The flux of each component is computed with $m = -2.5 \times \log({\rm flux})$, where $m$ is the integrated magnitude output from \textsc{Galfit}. There areWhen \textsc{Galfit} cannot find a core or an envelope, it will sometimes fit instead an extremely large and faint component instead. Where this happens (5 out of 124 cases), we classify this fit as either all core/envelope depending on which component was bad. We also see in 4 out of the 124 cases that the \Reff\ values for each component will be exactly the same value. When this occurs, we classify the galaxy as being all core.

\begin{figure*}[htbp]
\begin{center}
\includegraphics{Reff_Mstars.eps}
\caption{We plot here the deconvolved \Reff\ measurements for the}
\label{fig:radius}
\end{center}
\end{figure*}

\section{Methods}
\label{methods}

\subsection{Photometry: galaxy colors, stellar and baryonic masses, and star formation rates}
\label{phot}
\noindent The RESOLVE survey overlaps with a number of photometric surveys, including GALEX $NUV$ \citep{Morrissey2007}, SDSS-DR8 $ugriz$ \citep{Aihara2011}, and UKIDSS $YHK$ and/or 2MASS $JHK$ \citep{Skrutskie2006}. We reprocess this photometric data in a custom way in order to improve upon the standard SDSS pipeline photometry with improved sky subtraction following Blanton et al. (2011) and use additional sky subtraction for 2MASS and UKIDSS. and use it to derive galaxy colors, stellar and baryonic masses, and star formation rates. \citet{Eckert2015} describes in detail RESOVLE's custom reprocessing for these photometry, but the basic steps are described here.

Our reprocessed photometry improves over SDSS pipeline photometry in several key ways. First, we use images with improved sky subtraction coming from either Blanton et al. (2011) for SDSS or our own additional sky subtraction for 2MASS and UKIDSS. Second, we use the sum of the high S/N gri images to define the elliptical apertures, allowing us to determine the PA and axial ratio of the outer disk if present. Third, we apply these same elliptical apertures to all bands which allows us to measure magnitudes for galaxies that may not have been detected by the original automated survey pipeline in certain bands, especially low surface brightness galaxies in 2MASS, UKIDSS, and GALEX. Lastly, we use two to three non-parametric methods of total magnitude exrapolation, measuring the light from each band independently (see Figure 2 and 3.1.2). This last point allows for color gradients within galaxies, as opposed to the model magnitudes provided by SDSS (more details in 3.1.3), and allows us to measure systematic errors on magnitudes. We provide a comparison of the magnitudes, colors, and radii with photometry from the DR7 catalog of SDSS in Figure 3 and 3.1.3. Briefly summarizing, we find that the newly reprocessed photometry yields brighter magnitudes and larger effective radii. The colors tend to be bluer for large objects, which we believe to be a consequence of both the improved sky subtraction from Blanton et al. (2011) and the fact that we allow color gradients in magnitude estimation. The newly reprocessed photometry does not create a tight red sequence on the color-magnitude relation as seen in the DR7 photometry, however we argue that the tight red sequence may be a consequence of these two issues in ¤3.1.3. We also dis- cuss an independent validation of our methods with the NFGS survey (shown in Figure 2a of K13) in 3.1.3.

Stellar masses and star formation rates are then derived from these colors using the stellar population synthesis code described in

To calculate stellar masses and colors, we use the
spectral energy distribution (SED) modeling code described in Kannappan \& Gawiser (2007), Kannappan et al. (2009), and K13, which fits our newly reprocessed total NUVugrizY JHK magnitudes to a grid of stellar population models. With up to 9 or 10 bands of photo- metric data in ECO and RESOLVE-B respectively, we can estimate robust stellar masses. In RESOLVE-B we exclude the UKIDSS data if they are flagged due to sky background or image artifact issues (E15). We do not use UKIDSS J and we exclude H and K band data if they are fainter than 18 and 17.5 mag respectively. We exclude 2MASS JHK data if they are fainter than 16, 15, and 14.5mag respectively. We exclude any NUV data fainter than 24 mag. In this work we consider two model sets to determine
how robust the mass function shape is to changes in IMF and star formation history. Both model grids consist of an old and young population, yielding a composite stellar population (CSP), including an old population and

\subsection{Environmental Metrics}
\label{env}
\noindent RESOLVE is advantageous to this study because it offers excellent environment information, allowing us to search for CCGs in all environments including groups, clusters, walls, and filaments. We explore the environments of CCGs using two different metrics: the mass of their group halo and their distance to another galaxy. The group halo mass allows us to look for CCGs that are M32--Andromeda analogs where tidal stripping may be at play, or conversely look for CCGs in large groups where ram-pressure stripping could occur. The distance to neighboring galaxies lets us examine if interaction may occur or look for analogs of the isolated galaxies found by \citet{Huxor2013} and \citet{Paudel2014}.

Galaxy groups are identified using the friends-of-friends algorithm of \citet{Berlind2006}, and the masses of these group halos are calculated based on the observed total $r$-band luminosity of galaxies in each group using abundance matching, as described in \citet{Blanton2007}. More information on group identification can be found in \citet{Moffett2015}. The nearest neighbor distances are computed using the RA, Dec, and redshifts of each galaxy and along with spherical geometry principles.

@@

\subsubsection{SOAR spectroscopy}
\noindent The RESOLVE survey gets the bulk of its spectroscopic data from the SOuthern Astrophysical Research (SOAR) Telescope, located at Cerro Tololo, Chile. We employ the Goodman Spectrograph, designed and built by UNC, along with RESOLVE's custom-built image slicer with 3 $1''$ slits to observe galaxies in both a broad setup and either an emission- or absorption-line kinematic setup. With this absorption-line setup, we are able to derive velocity dispersions. We use the highly-efficient 2100 l/mm VPH grating in order to cover a wavelength range 4858-5503\AA, which includes stellar absorption lines such as H$\beta$, the magnesium triplet, and Fe5270/5335. To achieve S/N $\sim$ 25 per \AA, we bin each central spectrum to \Reff.

The reduction process is as follows: we use standard IRAF tasks to perform bias and overscan subtraction, trimming of the science data to remove unnecessary spatial coverage, and flat fielding. We then use \texttt{LA\_COSMIC} \citep{vanDokkum2001} to clean cosmic rays from each science exposure. We next complete a wavelength calibration and transformation, and then perform object tracing and extraction into a 1D spectrum using the IRAF task apall. We lastly combine the individual exposures using the IRAF task scombine.

@@

The spectral reduction proceeds as follows. Using the standard IRAF Gemini-GMOS data packages, bias and overscan subtraction, spatial trimming, flat fielding and fiber identification are performed. We next use the GMOS package gemCRspec, a wrapper for \texttt{LA\_COSMIC}, to clean cosmic rays from each science exposure. We then correct the science frames for quantum efficiency differences between CCDs. Wavelength transformation, sky subtraction, and flux calibration are subsequently performed, and lastly, data cubes are made and summed. We then stack the individual fiber spectra out to \Reff\ to create a 1D spectrum for each galaxy that has S/N $\sim25$. More information on the data reduction for the Gemini GMOS IFU can be found in  Appendix A.

@@

\noindent We then derive $\sigma$ from the both the SOAR and Gemini spectra using {\sc pPXF}, the penalized pixel fitting code from \citet{Cappellari2004}. This code fits a combination of high-resolution (FWHM $= 0.55$ \AA) ELODIE-based model spectra from \citet{Maraston2011} to the observed input spectrum, and determines a best fit solution for $\sigma$. A caveat to these fits is that they are not corrected for any stellar rotation, which will make absorption lines wider and thus skews the derived $\sigma$ values toward higher values depending on the amount of rotation in each galaxy. Future work will include implementing a stellar rotation subtraction routine for these fits, but preliminary testing by binning the spectra to $1''$ instead of to \Reff\ shows little change between the derived $\sigma$ values.

@@

\subsection{Colors and Star formation rates}

\begin{figure*}[t!]
\begin{center}
\includegraphics[scale=0.65]{sfr_mbary.eps}
\caption{default}
\label{flg:fsmgr}
\end{center}
\end{figure*}

\noindent The left side of \autoref{fig:envplot} shows the $u-r$ colors of our CCG sample plotted against M$_*$, compared to the RESOLVE sample as a whole. An unusual finding is that many CCGs live on the blue sequence, a previously rare color for CSSs. REF and REF have previously found UCDs in the blue cloud but most cEs and dEs are typically thought of as being "red and dead".

The right side of \autoref{fig:envplot} shows FSMGR vs. M$_{\rm bary}$ for the same objects. As with the colors, we find that many CCGs are forming stars at a rapid rate (> 1 per Gyr). This again goes against the common thought that CSSs are ``red and dead".

@@

\begin{figure*}[t]
\begin{center}
\includegraphics{nn_groupmass.eps}
\caption{default}
\label{fig:envplot}
\end{center}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{CCG formation and evolution} %kind of like a discussion section

@@

\begin{table*}[b]
\caption{default}
\begin{center}
\begin{tabular}{cccccccc}\hline \hline
\# & name & RA & Dec & core \Reff\ [pc] & envelope \Reff\ [pc] & $\chi^2/\nu$ & log(flux$_{core}$/flux$_{envelope}$) \\ \hline
1 & rs0003 & 133.68635 & 4.3019552 & 821.463 & 821.463 & 1.18600 & 1.00000  \\
2 & rs0178 & 149.91796 & 3.2930701 & 397.295 & 1406.25 & 1.16500 & -0.184240  \\
3 & rs0226 & 153.10508 & 1.2459080 & 632.824 & 3156.16 & 1.21900 & 0.297680  \\
4 & rs0241 & 155.57380 & 0.010365953 & 445.272 & 884.769 & 1.07200 & -0.904000 \\
5 & rs0246 & 155.77914 & 1.0061422 & 533.968 & 1056.30 & 1.08500 & 0.697800 \\
6 & rs0264 & 156.83775 & 0.42236355 & 489.703 & 1015.89 & 1.17800 & -0.292520 \\
7 & rs0284 & 158.11599 & 3.9140821 & 438.697 & 1239.27 & 1.16200 & -0.539200 \\
8 & rs0297 & 159.47069 & 4.8132268 & 712.400 & 768.898 & 1.07100 & -0.568280 \\
9 & rs0345 & 163.22317 & 4.5062644 & 414.999 & 966.451 & 1.06700 & -0.243041 \\
10 & rs0350 & 163.69943 & 2.9479643 & 772.270 & 1584.13 & 0.952000 & 0.394559 \\
11 & rs0364 & 165.21139 & 4.3915459 & 538.817 & 1612.12 & 1.16000 & -0.158081 \\
12 & rs0419 & 169.33097 & 2.8817070 & 252.336 & 1002.62 & 1.03500 & -0.111560 \\
13 & rs0422 & 169.39304 & 2.7726236 & 752.425 & 1189.52 & 1.09100 & 0.0501595 \\
14 & rs0424 & 169.54402 & 2.6007993 & 463.767 & 1092.22 & 1.18400 & -0.672560 \\
15 & rs0485 & 172.24999 & 3.8540120 & 584.173 & 803.029 & 1.17200 & -0.519680 \\
16 & rs0493 & 172.55178 & 3.8010930 & 837.815 & 849.963 & 1.04200 & -0.351080 \\
17 & rs0511 & 173.51621 & 2.9734660 & 650.023 & 1211.75 & 1.04000 & -0.101080 \\
18 & rs0529 & 174.73052 & 3.6007886 & 444.960 & 1989.59 & 1.18600 & -0.142760 \\
19 & rs0541 & 175.29068 & 4.6257403 & 560.561 & 1411.80 & 1.06800 & 0.846080 \\
20 & rs0559 & 176.80368 & 2.5339341 & 460.211 & 1210.71 & 1.11800 & -0.160679 \\
21 & rs0567 & 177.62803 & 1.9833304 & 203.049 & 2150.17 & 1.08800 & 0.165200 \\
22 & rs0586 & 179.25994 & 0.49846395 & 519.351 & 807.097 & 1.12600 & -0.110800 \\
23 & rs0596 & 180.30504 & 2.0499671 & 499.161 & 2119.90 & 1.08000 & 0.856960 \\
24 & rs0623 & 180.73707 & 1.3937952 & 475.008 & 1019.83 & 1.13200 & -0.307200 \\
25 & rs0640 & 180.90099 & 3.7565363 & 571.896 & 1138.14 & 1.14900 & -0.797760 \\
26 & rs0662 & 181.05450 & 1.9002092 & 800.801 & 1212.27 & 1.07800 & 0.867321 \\
27 & rs0663 & 181.06209 & 1.8667357 & 833.690 & 1576.26 & 1.09800 & 0.690200 \\
28 & rs0666 & 181.07212 & 1.9175187 & 432.492 & 432.492 & 0.998000 & 1.00000 \\
29 & rs0685 & 181.15300 & 1.8926987 & 270.945 & 471.503 & 1.02400 & -0.231679 \\
30 & rs0692 & 181.19149 & 1.8039932 & 299.521 & 1419.81 & 1.14800 & -0.238760 \\
31 & rs0693 & 181.19332 & 2.0052805 & 577.377 & 3597.03 & 1.10500 & 1.00000 \\
32 & rs0706 & 181.32842 & 1.6376421 & 186.636 & 854.695 & 1.06100 & -1.00000 \\
33 & rs0744 & 182.42105 & 0.65773495 & 361.692 & 915.910 & 1.00200 & 0.225360 \\
34 & rs0749 & 182.62971 & 0.67284561 & 404.559 & 501.619 & 0.703000 & 0.753240 \\
35 & rs0782 & 183.89462 & 1.2864481 & 450.290 & 848.580 & 1.11100 & -0.164360 \\
36 & rs0812 & 185.76816 & 3.6659076 & 492.992 & 2409.71 & 1.12600 & 1.31604  \\
37 & rs0814 & 185.81878 & 4.8360734 & 480.111 & 1499.67 & 1.15000 & 0.287200 \\
38 & rs0840 & 187.42097 & 0.25347730 & 641.957 & 919.368 & 1.09300 & 0.0679602 \\
39 & rs0862 & 187.93979 & 0.45263727 & 814.029 & 1199.91 & 1.17600 & 0.334680 \\
40 & rs0869 & 188.68743 & 0.36667434 & 352.165 & 1889.67 & 1.21200 & 0.109560 \\
41 & rs0906 & 191.31812 & 2.4491060 & 483.224 & 2456.56 & 1.11800 & 0.419680 \\
42 & rs0972 & 197.87107 & 3.6874893 & 730.731 & 889.397 & 1.00900 & 0.793440 \\
43 & rs0995 & 198.99419 & 2.9514062 & 836.917 & 2778.09 & 1.17400 & 0.653160 \\
44 & rs1001 & 199.42659 & 3.6036901 & 692.197 & 855.021 & 1.13400 & 0.111879 \\
45 & rs1053 & 201.81573 & 4.2087658 & 653.203 & 1401.12 & 1.10500 & 0.00380042 \\
46 & rs1091 & 203.50670 & 1.0961109 & 278.757 & 833.818 & 1.08000 & 0.361680 \\
47 & rs1094 & 203.52381 & 4.7805252 & 796.666 & 5662.08 & 1.09100 & 1.00000 \\
48 & rs1100 & 203.64064 & 4.9188438 & 817.006 & 914.505 & 1.05000 & -0.856239 \\
49 & rs1103 & 203.71245 & 4.2369242 & 358.480 & 1186.76 & 1.14700 & 0.175280 \\
50 & rs1128 & 204.34076 & 4.6890855 & 604.906 & 1514.74 & 1.17300 & 0.135961 \\
51 & rs1359 & 204.71440 & 4.4317127 & 513.871 & 1451.63 & 1.14900 & -0.0193595 \\
52 & rs1172 & 205.14099 & 4.8202809 & 385.743 & 927.874 & 1.12800 & -0.170840 \\
53 & rs1180 & 205.38541 & 4.1942047 & 603.266 & 1102.00 & 1.29500 & -0.188240 \\
54 & rs1186 & 205.49539 & 4.7635971 & 605.924 & 1193.42 & 0.968000 & 0.512960 \\
55 & rs1207 & 206.55280 & 3.5059126 & 432.668 & 1470.88 & 1.05300 & 0.281721 \\
56 & rs1208 & 206.60028 & 1.5787812 & 679.536 & 1019.00 & 1.24500 & -0.584320 \\
57 & rs1257 & 211.35992 & 3.0333434 & 657.017 & 928.701 & 1.09100 & -0.214119 \\
58 & rs1259 & 212.19482 & 4.9098567 & 340.962 & 982.659 & 1.12200 & -0.370719 \\
59 & rs1270 & 216.07293 & 4.6996761 & 587.943 & 1259.93 & 1.08200 & -0.164520 \\
60 & rs1291 & 224.22974 & 4.2051356 & 739.350 & 1137.16 & 1.22400 & 0.0689202 \\
61 & rs0287 & 158.77285 & 0.28142271 & 411.813 & 840.318 & 1.08800 & -0.803640 \\
62 & rs1453 & 200.69881 & 3.7793812 & 324.608 & 792.803 & 1.20200 & -0.284640 \\
63 & rs1456 & 205.20741 & 2.8178559 & 391.510 & 391.510 & 1.08600 & 1.00000 \\
64 & rf0518 & 2.2105393 & -1.1702019 & 465.731 & 2196.11 & 1.13900 & 0.114200 \\
65 & rf0003 & 2.3154592 & 0.81264576 & 686.760 & 686.760 & 0.971000 & 1.00000 \\
66 & rf0078 & 15.724560 & -0.31966061 & 355.476 & 1137.93 & 0.821000 & 0.300120 \\
67 & rf0563 & 16.109272 & -0.65961046 & 822.314 & 3972.25 & 1.17600 & 1.00000 \\
68 & rf0568 & 16.747559 & -0.59600971 & 552.735 & 1257.87 & 1.21100 & -0.313640 \\
69 & rf0143 & 18.353539 & 0.22052619 & 689.135 & 1033.19 & 1.08300 & -0.0775604 \\
70 & rf0154 & 18.903888 & -0.95294103 & 789.710 & 20578.8 & 1.12200 & 1.00000 \\
71 & rf0179 & 21.123601 & -0.36943684 & 549.049 & 2260.41 & 1.26300 & 0.585001 \\
72 & rf0195 & 21.478055 & -0.98781101 & 718.558 & 2522.79 & 1.16500 & 0.523720 \\
73 & rf0197 & 21.556976 & 0.35858673 & 245.635 & 686.455 & 1.08200 & -0.577440 \\
74 & rf0217 & 21.968796 & -0.50420076 & 801.105 & 27583.3 & 1.19900 & 1.00000 \\
75 & rf0229 & 22.801921 & -0.61075471 & 644.919 & 3473.07 & 1.10000 & 0.413480 \\
76 & rf0241 & 23.436054 & 0.95319263 & 623.932 & 945.284 & 1.20000 & 1.00000 \\
77 & rf0243 & 23.531574 & -1.0483175 & 681.056 & 1421.28 & 1.18200 & -0.148561 \\
78 & rf0247 & 23.786680 & 0.71782400 & 569.185 & 1700.14 & 1.14600 & 1.00000 \\
79 & rf0250 & 24.296472 & 0.88248657 & 486.472 & 10812.0 & 1.08600 & 1.00000 \\
80 & rf0253 & 24.678808 & -0.34802671 & 183.131 & 739.562 & 1.15800 & 0.0172801 \\
81 & rf0266 & 28.224302 & -0.90206277 & 181.014 & 693.328 & 1.18200 & -0.262840 \\
82 & rf0280 & 28.693912 & -0.73893120 & 513.218 & 27731.2 & 1.20300 & 1.00000 \\
83 & rf0663 & 34.464996 & 1.2245195 & 762.472 & 2440.96 & 1.19500 & 0.141921 \\
84 & rf0328 & 37.152547 & -0.24656214 & 442.135 & 1714.92 & 1.18400 & 0.339000 \\
85 & rf0332 & 37.413698 & 0.12338943 & 671.104 & 682.327 & 1.27800 & -0.486200 \\
86 & rf0340 & 37.926994 & 1.1969289 & 810.561 & 810.561 & 1.10000 & 1.00000 \\
87 & rf0352 & 38.090155 & 1.1750138 & 675.498 & 1220.81 & 1.13000 & 1.06556 \\
88 & rf0365 & 38.209305 & 0.66106589 & 384.276 & 682.691 & 1.12700 & -0.306679 \\
89 & rf0367 & 38.211703 & 1.1492129 & 471.387 & 1604.43 & 1.16400 & -0.0500407 \\
90 & rf0707 & 40.340884 & 0.058162170 & 464.822 & 1112.55 & 1.14000 & 0.304760 \\
91 & rf0392 & 41.594894 & -1.1714824 & 742.347 & 47400.9 & 1.21200 & 1.00000  \\
92 & rf0419 & 330.45871 & -0.70729601 & 447.720 & 1181.10 & 1.20200 & -0.706640 \\
93 & rf0479 & 353.17151 & -0.75714491 & 507.162 & 1799.10 & 1.18800 & -0.132120 \\
94 & rf0492 & 356.07298 & 0.44182044 & 232.505 & 1118.50 & 1.09600 & 0.00903985 \\
95 & rf0503 & 358.09449 & -0.62866731 & 356.736 & 2299.10 & 0.883000 & 0.314640 \\
96 & rf0505 & 358.63499 & -0.046906637 & 785.406 & 785.406 & 1.17100 & 1.00000 \\

\\ \hline\hline

\end{tabular}
\end{center}
\label{default}
\end{table*}%
